%                **** IMPORTANT NOTICE *****
% This LaTeX file has been automatically produced by ProTeX v. 1.1
% Any changes made to this file will likely be lost next time
% this file is regenerated from its source. Send questions 
% to Arlindo da Silva, dasilva@gsfc.nasa.gov
 
\setlength{\oldparskip}{\parskip}
\setlength{\parskip}{1.5ex}
\setlength{\oldparindent}{\parindent}
\setlength{\parindent}{0pt}
\setlength{\oldbaselineskip}{\baselineskip}
\setlength{\baselineskip}{11pt}
 
%--------------------- SHORT-HAND MACROS ----------------------
\def\bv{\begin{verbatim}}
\def\ev{\end{verbatim}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\bi{\begin{itemize}}
\def\ei{\end{itemize}}
\def\bn{\begin{enumerate}}
\def\en{\end{enumerate}}
\def\bd{\begin{description}}
\def\ed{\end{description}}
\def\({\left (}
\def\){\right )}
\def\[{\left [}
\def\]{\right ]}
\def\<{\left  \langle}
\def\>{\right \rangle}
\def\cI{{\cal I}}
\def\diag{\mathop{\rm diag}}
\def\tr{\mathop{\rm tr}}
%-------------------------------------------------------------

\markboth{Left}{Source File: ESMF\_FieldRegridMaskEx.F90,  Date: Tue May  5 21:00:02 MDT 2020
}

 
%/////////////////////////////////////////////////////////////

  
  \subsubsection{Field regrid with masking}
   As before, to create the sparse matrix regrid operator we call the
   {\tt ESMF\_FieldRegridStore()} routine. 
   However, in this case we apply masking to the regrid operation. 
   The mask value for each index location in the Grids may be set using
   the {\tt ESMF\_GridAddItem()} call (see Section~\ref{sec:usage:items}
   and Section~\ref{sec:usage:items:accessing}). Mask values may be set independently 
   for the source and destination Grids. If no mask values have been set in a Grid, then it is 
   assumed no masking should be used for that Grid. The {\tt srcMaskValues}
   parameter allows the user to set the list of values which indicate
   that a source location should be masked out. The {\tt dstMaskValues}
   parameter allows the user to set the list of values which indicate
   that a destination location should be masked out. The absence of 
   one of these parameters indicates that no masking should be used
   for that Field (e.g no {\tt srcMaskValue} parameter indicates that source
   masking shouldn't occur). The {\tt unmappedaction} flag may be
   used with or without masking and indicates what should occur
   if destination points can not be mapped to a source cell. 
   Here the {\tt ESMF\_UNMAPPEDACTION\_IGNORE} value indicates that unmapped
   destination points are to be ignored and no sparse matrix entries should be
    generated for them.  
%/////////////////////////////////////////////////////////////

 \begin{verbatim}
  call ESMF_FieldRegridStore(srcField=srcField, srcMaskValues=(/1/),       &
                             dstField=dstField, dstMaskValues=(/1/),       &
                             unmappedaction=ESMF_UNMAPPEDACTION_IGNORE, &
                             routeHandle=routeHandle,                      &
                             regridmethod=ESMF_REGRIDMETHOD_BILINEAR,     &
                             rc=localrc)
 
\end{verbatim}
 
%/////////////////////////////////////////////////////////////

  
   The {\tt ESMF\_FieldRegrid} and {\tt ESMF\_FieldRegridRelease} calls
   may then be applied as in the previous example.
%...............................................................
\setlength{\parskip}{\oldparskip}
\setlength{\parindent}{\oldparindent}
\setlength{\baselineskip}{\oldbaselineskip}
