%                **** IMPORTANT NOTICE *****
% This LaTeX file has been automatically produced by ProTeX v. 1.1
% Any changes made to this file will likely be lost next time
% this file is regenerated from its source. Send questions 
% to Arlindo da Silva, dasilva@gsfc.nasa.gov
 
\setlength{\oldparskip}{\parskip}
\setlength{\parskip}{1.5ex}
\setlength{\oldparindent}{\parindent}
\setlength{\parindent}{0pt}
\setlength{\oldbaselineskip}{\baselineskip}
\setlength{\baselineskip}{11pt}
 
%--------------------- SHORT-HAND MACROS ----------------------
\def\bv{\begin{verbatim}}
\def\ev{\end{verbatim}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\bi{\begin{itemize}}
\def\ei{\end{itemize}}
\def\bn{\begin{enumerate}}
\def\en{\end{enumerate}}
\def\bd{\begin{description}}
\def\ed{\end{description}}
\def\({\left (}
\def\){\right )}
\def\[{\left [}
\def\]{\right ]}
\def\<{\left  \langle}
\def\>{\right \rangle}
\def\cI{{\cal I}}
\def\diag{\mathop{\rm diag}}
\def\tr{\mathop{\rm tr}}
%-------------------------------------------------------------

\markboth{Left}{Source File: ESMF\_XGridGet.F90,  Date: Tue May  5 20:59:57 MDT 2020
}

 
%/////////////////////////////////////////////////////////////
\subsubsection [ESMF\_XGridGet] {ESMF\_XGridGet - Get object-wide information from an XGrid}


 
\bigskip{\sf INTERFACE:}
\begin{verbatim}   ! Private name; call using ESMF_XGridGet()
 
 subroutine ESMF_XGridGetDefault(xgrid, &
     sideAGridCount, sideBGridCount, sideAMeshCount, sideBMeshCount, &
     dimCount, elementCount, &
     sideAGrid, sideBGrid, sideAMesh, sideBMesh, &
     mesh, &
     area, centroid, &
     distgridA, distgridB, distgridM, &
     sparseMatA2X, sparseMatX2A, sparseMatB2X, sparseMatX2B, &
     name, &
     rc) 
 \end{verbatim}{\em ARGUMENTS:}
\begin{verbatim} type(ESMF_XGrid),     intent(in)            :: xgrid
 -- The following arguments require argument keyword syntax (e.g. rc=rc). --
 integer,              intent(out), optional :: sideAGridCount, sideBGridCount
 integer,              intent(out), optional :: sideAMeshCount, sideBMeshCount
 integer,              intent(out), optional :: dimCount
 integer,              intent(out), optional :: elementCount
 type(ESMF_Grid),      intent(out), optional :: sideAGrid(:), sideBGrid(:)
 type(ESMF_Mesh),      intent(out), optional :: sideAMesh(:), sideBMesh(:)
 type(ESMF_Mesh),      intent(out), optional :: mesh
 real(ESMF_KIND_R8),   intent(out), optional :: area(:)
 real(ESMF_KIND_R8),   intent(out), optional :: centroid(:,:)
 type(ESMF_DistGrid),  intent(out), optional :: distgridA(:)
 type(ESMF_DistGrid),  intent(out), optional :: distgridB(:)
 type(ESMF_DistGrid),  intent(out), optional :: distgridM
 type(ESMF_XGridSpec), intent(out), optional :: sparseMatA2X(:)
 type(ESMF_XGridSpec), intent(out), optional :: sparseMatX2A(:)
 type(ESMF_XGridSpec), intent(out), optional :: sparseMatB2X(:)
 type(ESMF_XGridSpec), intent(out), optional :: sparseMatX2B(:)
 character (len=*),    intent(out), optional :: name
 integer,              intent(out), optional :: rc \end{verbatim}
{\sf DESCRIPTION:\\ }


        Get information about XGrid
  
       The arguments are:
       \begin{description}
       \item [xgrid]
         The {\tt ESMF\_XGrid} object used to retrieve information from.
       \item [{[sideAGridCount]}]
             Total Number of Grids on the A side.
       \item [{[sideBGridCount]}]
             Total Number of Grids on the B side.
       \item [{[sideAMeshCount]}]
             Total Number of Meshes on the A side.
       \item [{[sideBMeshCount]}]
             Total Number of Meshes on the B side.
       \item [{[dimCount]}]
             Number of dimension of the xgrid.
       \item [{[elementCount]}]
            Number of elements in exclusive region of the xgrid on this PET.
       \item [{[sideAGrid]}]
             List of 2D Grids on side A. Must enter with shape(sideAGrid)=(/sideAGridCount/).
       \item [{[sideBGrid]}]
             List of 2D Grids on side B. Must enter with shape(sideBGrid)=(/sideBGridCount/).
       \item [{[sideAMesh]}]
             List of 2D Meshes on side A. Must enter with shape(sideAMesh)=(/sideAMeshCount/).
       \item [{[sideBMesh]}]
             List of 2D Meshes on side B. Must enter with shape(sideBMesh)=(/sideBMeshCount/).
       \item [{[mesh]}]
             Super mesh stored in XGrid when storeOverlay is set true during XGrid creation.
       \item [{[area]}]
             Area of the xgrid cells on this PET. Must enter with shape(area)=(/elementCount/).
       \item [{[centroid]}]
             Coordinates at the area weighted center of the xgrid cells on this PET. Must enter with shape(centroid)=(/elementCount, dimCount/).
       \item [{[distgridA]}]
             List of distgrids whose sequence index list is an overlap between a Grid
             on sideA and the xgrid object. Must enter with shape(distgridA)=(/sideAGridCount+sideAMeshCount/).
       \item [{[distgridB]}]
             List of distgrids whose sequence index list is an overlap between a Grid
             on sideB and the xgrid object. Must enter with shape(distgridB)=(/sideBGridCount+sideBMeshCount/).
       \item [{[distgridM]}]
             The distgrid whose sequence index list fully describes the xgrid object.
       \item [{[sparseMatA2X]}]
             Indexlist from a Grid index space on side A to xgrid index space; 
             indexFactorlist from a Grid index space on side A to xgrid index space. Must enter with shape(sparsematA2X)=(/sideAGridCount+sideAMeshCount/).
       \item [{[sparseMatX2A]}]
             Indexlist from xgrid index space to a Grid index space on side A; 
             indexFactorlist from xgrid index space to a Grid index space on side A. Must enter with shape(sparsematX2A)=(/sideAGridCount+sideAMeshCount/).
       \item [{[sparseMatB2X]}]
             Indexlist from a Grid index space on side B to xgrid index space; 
             indexFactorlist from a Grid index space on side B to xgrid index space. Must enter with shape(sparsematB2X)=(/sideBGridCount+sideBMeshCount/).
       \item [{[sparseMatX2B]}]
             Indexlist from xgrid index space to a Grid index space on side B; 
             indexFactorlist from xgrid index space to a Grid index space on side B. Must enter with shape(sparsematX2B)=(/sideBGridCount+sideBMeshCount/).
       \item [{[name]}]
             Name of the xgrid object.
       \item [{[rc]}]
             Return code; equals {\tt ESMF\_SUCCESS} only if the {\tt ESMF\_XGrid} 
             is created.
       \end{description}
  
%...............................................................
\setlength{\parskip}{\oldparskip}
\setlength{\parindent}{\oldparindent}
\setlength{\baselineskip}{\oldbaselineskip}
